---
output: rmarkdown::github_document
---
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active) 
[![Build Status](https://travis-ci.org/hrbrmstr/darksky.svg)](https://travis-ci.org/hrbrmstr/darksky) [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/darksky)](https://cran.r-project.org/package=darksky) ![downloads](http://cranlogs.r-pkg.org/badges/grand-total/darksky)

`darksky` : Tools to Work with the Dark Sky API

- Dark Sky API Docs: https://darksky.net/dev/docs
- Dark Sky Dev site: https://darksky.net/dev/

The following functions are implemented:

- `darksky_api_key` :	Get or set `DARKSKY_API_KEY` value
- `get_current_forecast` : Retrieve the current forecast (for the next week)
- `get_forecast_for` : Retrieve weather data for a specific place/time
- `plot.darksky` : Plot method for `darksky` objects
- `print.darksky` : A tad more human readable default printing

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/darksky")
```

OR

```{r eval=FALSE}
devtools::install.packages("darksky")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(darksky)
library(purrr)

# current verison
packageVersion("darksky")

now <- get_current_forecast(43.2672, -70.8617)
print(now)

then <- get_forecast_for(43.2672, -70.8617, "2013-05-06T12:00:00-0400", add_headers=TRUE)
print(then)

# getting data for more than one location

more_than_one <- data.frame(loc=c("Maine", "Seattle"),
                            lon=c(43.2672, 47.6097),
                            lat=c(70.8617, 122.3331),
                            when=c("2013-05-06T12:00:00-0400",
                                   "2013-05-06T12:00:00-0400"),
                            stringsAsFactors=FALSE)

bigger_list <- pmap(list(more_than_one$lon, more_than_one$lat,
                         more_than_one$when),
                    get_forecast_for)
names(bigger_list) <- more_than_one$loc

bigger_list$Seattle

bigger_list$Maine

print(sprintf("You have used %s API calls.", then$`x-forecast-api-calls`))

plot(now)
```

### Test Results

```{r}
library(darksky)
library(testthat)

date()

test_dir("tests/")
```

